---
title: "assignment 1"
output: pdf_document
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[CO,CE]{Group 9}
- \fancyfoot[CO,CE]{https://github.com/KazuMaeshima/Group-9-.git}
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggpubr)
library(tidyverse)
library(janitor) # janitor helps us clean datasets
library(here) # here helps us to know where files are
library(readxl)
```

## Load data
avocado=read.csv(file ="https://github.com/KazuMaeshima/Group-9-/raw/main/avocado.csv", header =TRUE)
##Provide a introduction of your analysis in the .RMD file so it can be produced in the output
# this codes will introduce us how to use R Studio as part of our day to day data analysis. It will produce variables, mean,median,mode, show and manipulate data and plot graphs using ggplot2
## head
## Print the structure of your dataset.
```{r}
 print(avocado)
```


##List the variables in your dataset
```{r}
 names(avocado)
```


##Print the top 15 rows of your dataset.
```{r}
 head(avocado,15)
```


##Write a user defined function using any of the variables from the data set
  
```{r}
m <- c(45,34,34,34,67)
  getmode <- function(m) {
   uniqv <- unique(m)
   uniqv[which.max(tabulate(match(m, uniqv)))]
 }
  getmode(m)
```
 

##Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset
```{r}
 filter(Avocado,AveragePrice<1)
```

##Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variablesfrom your dataset.\
# Create a new dataset with the selected columns
```{r}
 bags <- as.data.frame(avocado %>% select(Total.Bags,Small.Bags,Large.Bags,XLarge.Bags))
```


##Remove missing values in your dataset.
```{r}
na.omit(Avocado)
```

 
##Identify and remove duplicated data in your dataset.
```{r}
 avocado[!duplicated(avocado), ]
```


##Reorder multiple rows in descending order
```{r}
avocado %>% arrange(desc(AveragePrice))
```


##Rename some of the column names in your dataset.
```{r}
 head(avocado)
 m <- avocado
 dim(m)
 col_name <- paste("Col", 1:14, sep = "")
 head(m)
 names(m) <-col_name
 head(m)

```


##Add new variables in your data frame by using a mathematical function (for e.g. –multiply an existing column by 2 and add it as a new variable to your data frame)
##Create new variable by mutliplying an existing column by 2
```{r}
 avocado$Doubleyear = avocado$year*2
```
 

 
##Create a training set using random number generator engine.
 # Initiate random number generator engine
```{r}
 set.seed(1234)
```
 


## Select 80% rows from the main dataset as the training set
```{r}
training = avocado %>% sample_frac(0.8,replace=FALSE)
```

 
 
 
#Print the summary statistics of your dataset.
 
```{r}
 summary(avocado)
```



             
##Use any of the numerical variables from the dataset and perform the following statistical functions. Mean
```{r}
 mean(avocado$Large.Bags)
```



##Median
```{r}
median(avocado$Total.Bags)
```

 

##Mode
```{r}
 v <- c(avocado$AveragePrice) 
 # Calculate the mode using the user defined function
 result <- getmode(v)
 print(result)
```



##Range
```{r}
 range(avocado$Total.Bags)
```



##Plot a scatter plot for any 2 variables in your dataset.
```{r}
 ggplot(data = avocado, aes(x = Total.Bags, y=AveragePrice))+geom_point()
```



##Plot a bar plot for any 1 variables in your dataset
```{r}
ggplot(data = avocado, aes(x = AveragePrice))+geom_bar()
```

 

##Find the correlation between any 2 variables by applying least square linear regression model.
```{r}
 library(ggpubr)
 
 ggscatter(avocado, x="Total.Bags", y="AveragePrice", add="reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson", xlab = "Total Bags",ylab = "Average Price")
```



##Provide a conclusion of your analysis if any in the .RMD file.
#there are different types of avocados. Each avocados corresponds with their respective price based on their size and each country prices their avocados differently








